### 2020-05-04 LaTeX/sections/paper.tex
Updates: Code, testcase, cost table (using static arrays)

>>>>

%============= Ghazal with Auction Costs Table==================== %
\begin{table}[t]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{\shortstack{Number \\of \\Buy Orders}} & \textbf{\shortstack{Number \\of \\Sell Orders}} & \textbf{\shortstack{Total Number \\of\\ Orders}}  & \textbf{\shortstack{Gas Cost \\in\\ Ether}}  \\ \hline
1 & 1 & 2 & 144,689 \\
3 & 3 & 6 & 324,457 \\
5 & 5 & 10 & 527,289 \\
7 & 7 & 14 & 710,050 \\
9 & 9 & 18 & 964,894 \\
11 & 11 & 22 & 1,176,905 \\
13 & 13 & 26 & 1,370,191 \\
15 & 15 & 30 & 1,650,273 \\
17 & 17 & 34 & 1,953,406 \\
19 & 19 & 38 & 2,205,141 \\
21 & 21 & 42 & 2,416,221 \\
23 & 23 & 46 & 2,713,313 \\
25 & 25 & 50 & 1,788,509 \\
27 & 27 & 54 & 2,004,824 \\

\hline
29 & 29 & 58 & \textbf{out of gas}\\
\hline
\end{tabular}
\caption{\footnotesize{Gas used for Match function when using fixed arrays to store the heap.}\label{}}
\end{table}
%======================================== %
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
